Squint: Lossy Hierarchical Compression on Symbol Streams

### 2012-12-11 tex/paper.tex
Reflow and kill trailing whitespace

\documentclass[11pt]{article}
\usepackage{amsfonts,amsmath,amssymb,amsthm}
\usepackage{array}
\usepackage{bm}
\usepackage{commath}
\usepackage{enumitem}
\usepackage{fancyhdr,fancyvrb}
\usepackage[letterpaper,text={7in,9in},centering]{geometry}
\usepackage[pdftex]{graphicx}
\usepackage[lofdepth,lotdepth]{subfig}
\usepackage{ifthen}
\usepackage{mathrsfs}
\usepackage{multicol}
\usepackage{pifont}
\usepackage{sectsty}
\usepackage{setspace}
\usepackage{stackrel}
\usepackage{stmaryrd}
\usepackage{tensor}
\usepackage{xspace}
\usepackage{natbib}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{listings}
\usepackage{hyperref}
\lstset{basicstyle=\ttfamily\footnotesize,breaklines=true}

@@

@@

\begin{abstract}
Grammar-based compression schemes like \Sequitur exploit repeated structures
in streams of symbolic data to achieve good compression ratios.
We develop a set of algorithms for improving upon Grammar-based compression 
schemes by allowing some loss in the compression. Although precise 
subsequences might be altered, in return we can simplify 
the grammars produced to obtain better ratios while still preserving
important syntatic patterns at both the micro and macro level.
\end{abstract}

@@

\section{Introduction and Goals}
Many sources of data exhibit natural hierarchical structure. For instance,
english text often can be grouped well into sections, paragraphs, sentences, ...
all the way down to words and phonemes. Music too, consists of repeated motifs,
phrases, themes, and so on. Finally, computer code is so hierarchical that its
syntax can usually be put in BNF. This allows grammar-based compression schemes
to build up Context Free Grammars (CFGs) and achieve very good compression
ratios.

@@

\subsection{Grammar Compression}
As described in the introduction, the proposed research shares many of its
goals with the \Sequitur algorithm described in \cite{sequitur}.  The authors
of \cite{sequitur} develop an effective algorithm based on iteratively
rewriting grammars to keep them small and efficient, and produce interesting
grammar-based analyses of texts and musical scores.

@@

\begin{itemize}
\item Infer a CFG representation of a stream (possibly using Sequitur)
\item Simplify the CFG, possibly introducing loss
\item Output the CFG
\end{itemize}

@@

\begin{figure}[t]
\centering
\includegraphics[scale=0.6]{sred1.pdf}
\includegraphics[scale=0.6]{sred2.pdf}
\caption{Grammar Simplification Example}
\label{sred}
\end{figure}

@@

$$\frac{levenshtein(expand(rhs_1),expand(rhs_2))}
        {max(len(expand(rhs_1)),len(expand(rhs_2)))} < \epsilon$$.

@@

$$lsim(s1,s2) = \frac{levenshtein(s1,s2)}{max(len(s1),len(s2))}$$

@@

\subsection{Runtime Analysis}
Given an input of length $n$, let $r$ be the number of rules generated
by Sequitur from the input. 
In the analysis of the Similarity algorithm, let $R$ be the total number of variable
replacements we perform. For each replacement, we had to have searched though
up to all pairs of variables, and for each pair of variables expanding
them and calculating the levenshtein distance could take time linear in $n$.
Performing the replacement only takes time linear in $r$.
Thus the runtime is $\boxed{O(R*r^2*n)}$.

From the \Sequitur paper \cite{sequitur} we
know that the number of rules in the grammar generated by Sequitur
is between $O(1)$ and $O(n)$. Thus the worst case runtime on the similarity
algorithm is $\boxed{O(n^4)}$. This is because we could have up to $r$ replacements.
However, in practice we will see that the runtime is much better
than $O(n^4)$. There are a variety of possible reasons for this:
in our test data, $r$ didn't grow quite linearly in $n$, $R$ could grow much
slower than $r$, and the use of native code in calculating the levenshtein distance 
made the its contribution much less noticeable for the input sizes we tested.

@@

\section{Implementation}
Overview

\subsection{Grammar Reductions}
What is their purpose? Why do we want them? What are they?
Grammar reductions are a way of taking a CFG, generated possibly through
ad-hoc techniques, and systematically removing internal redundancies
like duplicate bigrams in Sequitur. They make the CFG representation smaller
but don't introduce any loss. We want them since our lossifier algorithms
often make our grammars redundant, even though the each step we take
in the lossifier makes the grammars smaller.

\subsection{Data Structures and Optimizations}
Grammar Data Structure
Cluster Data Structure
Invariants Maintained
Core utility methods??
Linked Lists vs Arrays, Caching Expansions, Strings vs Symbols for expansion, Native Levenshtein

\section{Results}
\subsection{Illustrative Examples}
It is useful to look at how the algorithms function on a small piece of
data with both plenty of hierarchical structure, and also some messiness
that most lossless compression schemes would not deal well with. Take
the string below, similar to what one might come across in a math
puzzle book.

@@

When comparing grammars, we chose to define the \emph{size} of a grammar
as the sum of the lengths of the rhs's of the production rules.
Sequitur yields a relatively complicated inferred grammar with 13 rules and
a size of 51. Both the Similarity and Clustering Algorithms with $\epsilon = .4$
, yield the following grammar after reduction. It has 5 rules and is almost
half the size, at 30.

@@

\subsection{Similarity vs Clustering}
For most of our benchmark tests, we focused on two extreme kinds of data:
one with large amounts of repetition at all levels, and one with a word
and sentence level structure but with little obvious large-scale repetition.
One set of test data was constructed by repeating the same letter `a' n-times
but then adding some
texture to the data by changing 1/30 of the characters uniformly
at random to `*'. Call these test-cases \emph{rep-n}
Another set of test data was constructed from the first n characters of the
book of Genesis from the KJV version of the Bible. 
Call these test-cases \emph{gen-n}

@@

In table \ref{simclus_r_t} we report the results on running Sequitur 
and Cluster, without
the grammar reductions, on the rep-n datasets. Time is the wall clock
running as measured on a 2.26 Ghz Intel Core 2 Duo Macbook Pro.
Ratio is the relative size of the grammar produced compared with
Sequitur, where the size of the grammar is the sum of the lengths of the
rhs's of the rules. Levdistance is the levenshtein distance between
the output of the lossified grammar and the original input string, it
is a kind of measure of the fidelity of our algorithms but doesn't
take into account how well patterns were preserved. For the rep-n tests,
proportion is the proportion of the final string produced that was
`*'. The closer to 1/30~0.033, the more accurate the lossifier was
in recreating the original texture of the input.

@@

The actual compression ratio was respectable, with both
Similarity and Cluster coming in at nearly half the size of the Sequitur CFG.
Setting higher values for $\epsilon$ had diminishing returns for compression
for larger and larger file sizes, at the cost of drastically lowering the fidelity
of the output.

@@

Repeating the above tests on the \emph{gen-n} datasets yields the results in table
\ref{simclus_g_t}

@@

\subsection{Grammar Reduction Impact}
Although the grammars generated by Sequitur are irreducible,
our lossifiers produce grammars which could potentially be
compressed further (losslessly) using Reduction Rules without
changing the output string. To test the cost and
effectiveness of applying reduction rules, we looked at the
rep-n and gen-n test cases again, this time focusing on the
clustering algorithm for $\epsilon = .2$. This time we give the ratio
on top of the simplified grammar produced by the clustering algorithm,
and the time taken to run just the reduction rules.

@@

The first piece of text is from the gen-n dataset again, the first 256000 characters
of the book of Genesis. As listed in table \ref{seqclus_g_t}, the compressed grammar
was size 5540 compared with Sequitur's size of 8060. Without knowledge of English 
spelling, the Cluster algorithm produces output that is hard to read. However,
key words are clearly recognizable, especially important words such as `God', and
the overall structure in the book of Genesis is retained.

@@

\section{Conclusions}
\subsection{Summary of Results}
* General concept of simplifying grammars, two proposed algorithms
* reasonably efficient implementation with runtime better than expected
* compared algorithms, evaluated effectiveness of reducer
* looked at effect of epsilon

@@

\begin{lstlisting}
#include<stdio.h>
#define c(C) printf("%c",C)
#define C(c) ((int*)(C[1]+6))[c]
main(int c,char    
*C[])         {(C[c]=C[
1]+2   )[0]=   c(52*c(\
'C'+  '4'/4)    );for(c
=0;  c<491;++   c)for(*
*C=  C[1]['c'    +c]  =
0;*   C[0]<8;(    **  C
)++    )C[1][c+   'c']=
*(C[  1]+c+'c')+  C[1][
99+    c]+(C[1    ][**C
+8*c  +99]==32    );  (
*C)[4]=*C[2]==    75  ?
*((C[2]+=3)-2    )==70?
1:0:0;C(0)=C(    1)=c=0
;while(*C[2]?   C[2][1]
?*(C[2]+2)?1    :0:0:0)
{if( *C [2      ]>'w'){
C(1)=0;C[1]    [2]++;*C
[2]=0;}else   C(1)+=*C[
2]==58?2+(    C[2][3]&&
*(C[2]+3)<   'x'):*C[2]
=='s'?(C[   2][1]-=48):
*C[2]>=65  ?3-(*C[2]==\
'm'?1:0)  :1;C(0)=C(1)>
C(0)?C(1  ):C(0);c+=3;*
(C+2)+=3;}printf("  %d\
          %d\n",        56+8*C(    0),80**(C[3]    ++))
         ;*C[2]=0       ;C[2]       -=c;*C[3]       =0;
        while(C[3]      [1,-         1]--){;   for(  **
        C=0     ;*      *C<          80;(**   C)++)  {C
       [2]      -=3     **           C[3];   *C[3]   ++
       =0;      *C[     3]          =**C>=  51||*   *C<
       18       ||*     *C         %8!=2?0  :255   ;c(1
       -1       );c     (*C       [3]);for(       (*C)[
       1]      =0;(     *C)[    1]<3;(*C)[1]    ++)c(*C
       [3      ]|((     *C)[  4]?**C>18&&* *C<42 ?C[1][
       42     +*(*      C+1)    +3***C]:0: **C>=  11&&*
       *C     <64?      ~C[1 ][   7***C+97 +(*C)[  1]]:
        0)   );c(       *C[3 ]++)   ;for(C (1)=0;   (C(
        2)   =C(1       ))<C (0);)   {(*C) [2]=C   [2][
        1]  -49;        c=(* C[2]<=   63); c=(*   C)[0]
        -4  *(C[        3][0 ]=105-  C[2][ c]   -7*(*(C
        [2]+c)<         'c') -18*(  C[2][c    ]<77)+2*(
         *C)[4          ]-7* (C[2] [c]<'C'  ))-6;for(C(
        3)=0;                                          
       C(3)<                                (*C[2]?*C[2
      ]>'r'                             ?C[    2][1]:(1
     +2*(*C             [2]>   64)    +(2-!C[2    ][3])
    *(58 ==             (*(C         +2))[0])-         
    (C[2] [0            ]=='m'   )  ):C(2)?C(0     )-C(
  2):0  );C(3)++)       C(1)+=c(C  [1][4]|(*     C[2]&&
 *C[2  ]<'s'?*C[2]      ==58?C(3)  ==1?**C     >17&&**C
 <51  ?C[ 2]    [1]     ==59?39:  C[2][1     ]==58?9:1:
0:0  :63  >*     C[2    ]?(c<7&&  c>-9?C[1    ][(*C[2]<
45?  'c'  *5     +2*    '%':*C[   2]<  61?570    :571)+
3*c  ]:   0)      :*C   [2]>'o'  ?**C>26&&**C<29    &&!
(*C  )[    2]     ||(   *C)[2]  ==1&&(&*C[0])       [0]
 <34  &&   31     <**   C?C(3)  <2?15+225*C(3     ):0:(
 *C)[  2]  ==     3?C   (3)<2  &&**C>22&&**C     <45&&C
 (3)<      2?     C[    1][7*  *(*C)+151+C      (3)]:0:
  7==(     *C    )[2    ]&&*  *C>26&&**C       <42&&C(3
  )<2?C    [1   ][7     ***C  +135+C(3)]       :0:*C[2]
   <'k'?    (c >-5                      &&      c<5?C(3
    )<2?C   [1][(                       (*C)     [2]<3?
     207:205)+7*                        c+C(3     )]:C[
      2][2]==46               &&        (c==-2||   c==-
            1-                          2*(*C[3]%2  ))?
            96                          :0:0)|((*C)[2  
             ]?                                        
             C(         3      )        ?C(3)< 2       
             &&                        *C[3]>  7   &&  
             c<           1&&c  >-24  ?8:0:*   C       
             [3         ]<8&&c  >1   &&c<24    ?   ' ' 
        :0   :0)        |(C(3) <2     &&(  **  C       
       ==66   &&        *C[3   ]>14   ||*  C[  3       
       ]>12   &&        58   ==**C||   *               
       C[3    ]<        2  &&**C==10   )            ?  
        5*  51:                       0)|(7==  (       
         *C)[                        2]?*C[3]  <       
8?c>13&& c<23&&C(3)<2?C
[1][144+ 7*c+C(3)]:0:C(
3) && c< -14&&c>- 24?C[
1] [7 *c +400+C(3 )]:0:
0) :! C  (3)?**C> 21&&C
[0 ][    0]   <32      
?C     [ 1 ]   [(      
*   C )    [2   ] +323 
   +7     **   *C ]:36 
 + 1   < **   C&& '0'> 
*     *C ?  C[1][      
   C[ 2]  [2]+162      
 + 7* **C]:0:0:0));C[1 
][ 3] ++;C[2]+=3;}c(0) 
;C [3 ]-=2;}*C[3]=0;}}

>>>>

\documentclass[11pt]{article}
\usepackage[letterpaper,text={7in,9in},centering]{geometry}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{amsfonts,amsmath,amssymb,amsthm}
\usepackage{array}
\usepackage{fancyhdr,fancyvrb}
\usepackage[pdftex]{graphicx}
\usepackage{hyperref}
\usepackage{listings}
\usepackage{natbib}
\usepackage[lofdepth,lotdepth]{subfig}
\usepackage{sectsty}
\usepackage{setspace}
\usepackage{stackrel}
\usepackage{xspace}

@@

\lstset{basicstyle=\ttfamily\footnotesize,breaklines=true}

@@

\begin{abstract}

Grammar-based compression schemes like \Sequitur exploit repeated structures in
streams of symbolic data to achieve good compression ratios.  We develop a set
of algorithms for improving upon Grammar-based compression schemes by allowing
some loss in the compression. Although precise subsequences might be altered,
in return we can simplify the grammars produced to obtain better ratios while
still preserving important syntatic patterns at both the micro and macro
levels.

\end{abstract}

@@

\section{Introduction and Goals}

Many sources of data exhibit natural hierarchical structure. For instance,
english text often can be grouped well into sections, paragraphs, sentences,
...  all the way down to words and phonemes. Music too, consists of repeated
motifs, phrases, themes, and so on. Finally, computer code is so hierarchical
that its syntax can usually be put in BNF. This allows grammar-based
compression schemes to build up Context Free Grammars (CFGs) and achieve very
good compression ratios.

@@

\subsection{Grammar Compression}

As described in the introduction, the proposed research shares many of its
goals with the \Sequitur algorithm described in \cite{sequitur}.  The authors
of \cite{sequitur} develop an effective algorithm based on iteratively
rewriting grammars to keep them small and efficient, and produce interesting
grammar-based analyses of texts and musical scores.

@@

\begin{itemize}
  \item Infer a CFG representation of a stream (possibly using \Sequitur)
  \item Simplify the CFG, possibly introducing loss
  \item Output the CFG
\end{itemize}

@@

\begin{figure}[t]
\centering
\includegraphics[scale=0.6]{include/sred1.pdf}
\includegraphics[scale=0.6]{include/sred2.pdf}
\caption{Grammar Simplification Example}
\label{sred}
\end{figure}

@@

\[
  \frac{levenshtein(expand(rhs_1),expand(rhs_2))}
      {max(len(expand(rhs_1)),len(expand(rhs_2)))} < \epsilon
\]

@@

\[ lsim(s1,s2) = \frac{levenshtein(s1,s2)}{max(len(s1),len(s2))} \]

@@

\subsection{Runtime Analysis}

Given an input of length $n$, let $r$ be the number of rules generated by
\Sequitur from the input.  In the analysis of the Similarity algorithm, let $R$
be the total number of variable replacements we perform. For each replacement,
we had to have searched though up to all pairs of variables, and for each pair
of variables expanding them and calculating the levenshtein distance could take
time linear in $n$.  Performing the replacement only takes time linear in $r$.
Thus the runtime is $\boxed{O(R*r^2*n)}$.

From the \Sequitur paper \cite{sequitur} we know that the number of rules in
the grammar generated by \Sequitur is between $O(1)$ and $O(n)$. Thus the worst
case runtime on the similarity algorithm is $\boxed{O(n^4)}$. This is because
we could have up to $r$ replacements.  However, in practice we will see that
the runtime is much better than $O(n^4)$. There are a variety of possible
reasons for this: in our test data, $r$ didn't grow quite linearly in $n$, $R$
could grow much slower than $r$, and the use of native code in calculating the
levenshtein distance made the its contribution much less noticeable for the
input sizes we tested.

@@

\section{Implementation}

Overview

\subsection{Grammar Reductions}

What is their purpose? Why do we want them? What are they?  Grammar reductions
are a way of taking a CFG, generated possibly through ad-hoc techniques, and
systematically removing internal redundancies like duplicate bigrams in
\Sequitur. They make the CFG representation smaller but don't introduce any
loss. We want them since our lossifier algorithms often make our grammars
redundant, even though the each step we take in the lossifier makes the
grammars smaller.

\subsection{Data Structures and Optimizations}

Grammar Data Structure
Cluster Data Structure
Invariants Maintained
Core utility methods??
Linked Lists vs Arrays, Caching Expansions, Strings vs Symbols for expansion, Native Levenshtein

\section{Results}

\subsection{Illustrative Examples}

It is useful to look at how the algorithms function on a small piece of data
with both plenty of hierarchical structure, and also some messiness that most
lossless compression schemes would not deal well with. Take the string below,
similar to what one might come across in a math puzzle book.

@@

When comparing grammars, we chose to define the \emph{size} of a grammar as the
sum of the lengths of the rhs's of the production rules.  \Sequitur yields a
relatively complicated inferred grammar with 13 rules and a size of 51. Both
the Similarity and Clustering Algorithms with $\epsilon = .4$ , yield the
following grammar after reduction. It has 5 rules and is almost half the size,
at 30.

@@

\subsection{Similarity vs Clustering}

For most of our benchmark tests, we focused on two extreme kinds of data: one
with large amounts of repetition at all levels, and one with a word and
sentence level structure but with little obvious large-scale repetition.  One
set of test data was constructed by repeating the same letter `a' n-times but
then adding some texture to the data by changing 1/30 of the characters
uniformly at random to `*'. Call these test-cases \emph{rep-n} Another set of
test data was constructed from the first n characters of the book of Genesis
from the KJV version of the Bible.  Call these test-cases \emph{gen-n}

@@

In table \ref{simclus_r_t} we report the results on running \Sequitur and
Cluster, without the grammar reductions, on the rep-n datasets. Time is the
wall clock running as measured on a 2.26 Ghz Intel Core 2 Duo Macbook Pro.
Ratio is the relative size of the grammar produced compared with \Sequitur,
where the size of the grammar is the sum of the lengths of the rhs's of the
rules. Levdistance is the levenshtein distance between the output of the
lossified grammar and the original input string, it is a kind of measure of the
fidelity of our algorithms but doesn't take into account how well patterns were
preserved. For the rep-n tests, proportion is the proportion of the final
string produced that was `*'. The closer to 1/30~0.033, the more accurate the
lossifier was in recreating the original texture of the input.

@@

The actual compression ratio was respectable, with both Similarity and Cluster
coming in at nearly half the size of the \Sequitur CFG.  Setting higher values
for $\epsilon$ had diminishing returns for compression for larger and larger
file sizes, at the cost of drastically lowering the fidelity of the output.

@@

Repeating the above tests on the \emph{gen-n} datasets yields the results in
table \ref{simclus_g_t}.

@@

\subsection{Grammar Reduction Impact}

Although the grammars generated by \Sequitur are irreducible, our lossifiers
produce grammars which could potentially be compressed further (losslessly)
using Reduction Rules without changing the output string. To test the cost and
effectiveness of applying reduction rules, we looked at the rep-n and gen-n
test cases again, this time focusing on the clustering algorithm for $\epsilon
= .2$. This time we give the ratio on top of the simplified grammar produced by
the clustering algorithm, and the time taken to run just the reduction rules.

@@

The first piece of text is from the gen-n dataset again, the first 256000
characters of the book of Genesis. As listed in table \ref{simclus_g_t}, the
compressed grammar was size 5540 compared with \Sequitur's size of 8060.
Without knowledge of English spelling, the Cluster algorithm produces output
that is hard to read. However, key words are clearly recognizable, especially
important words such as `God', and the overall structure in the book of Genesis
is retained.

@@

\section{Conclusions}

\subsection{Summary of Results}

* General concept of simplifying grammars, two proposed algorithms
* reasonably efficient implementation with runtime better than expected
* compared algorithms, evaluated effectiveness of reducer
* looked at effect of epsilon

@@

\begin{lstlisting}
#include<stdio.h>
#define c(C) printf("%c",C)
#define C(c) ((int*)(C[1]+6))[c]
main(int c,char
*C[])         {(C[c]=C[
1]+2   )[0]=   c(52*c(\
'C'+  '4'/4)    );for(c
=0;  c<491;++   c)for(*
*C=  C[1]['c'    +c]  =
0;*   C[0]<8;(    **  C
)++    )C[1][c+   'c']=
*(C[  1]+c+'c')+  C[1][
99+    c]+(C[1    ][**C
+8*c  +99]==32    );  (
*C)[4]=*C[2]==    75  ?
*((C[2]+=3)-2    )==70?
1:0:0;C(0)=C(    1)=c=0
;while(*C[2]?   C[2][1]
?*(C[2]+2)?1    :0:0:0)
{if( *C [2      ]>'w'){
C(1)=0;C[1]    [2]++;*C
[2]=0;}else   C(1)+=*C[
2]==58?2+(    C[2][3]&&
*(C[2]+3)<   'x'):*C[2]
=='s'?(C[   2][1]-=48):
*C[2]>=65  ?3-(*C[2]==\
'm'?1:0)  :1;C(0)=C(1)>
C(0)?C(1  ):C(0);c+=3;*
(C+2)+=3;}printf("  %d\
          %d\n",        56+8*C(    0),80**(C[3]    ++))
         ;*C[2]=0       ;C[2]       -=c;*C[3]       =0;
        while(C[3]      [1,-         1]--){;   for(  **
        C=0     ;*      *C<          80;(**   C)++)  {C
       [2]      -=3     **           C[3];   *C[3]   ++
       =0;      *C[     3]          =**C>=  51||*   *C<
       18       ||*     *C         %8!=2?0  :255   ;c(1
       -1       );c     (*C       [3]);for(       (*C)[
       1]      =0;(     *C)[    1]<3;(*C)[1]    ++)c(*C
       [3      ]|((     *C)[  4]?**C>18&&* *C<42 ?C[1][
       42     +*(*      C+1)    +3***C]:0: **C>=  11&&*
       *C     <64?      ~C[1 ][   7***C+97 +(*C)[  1]]:
        0)   );c(       *C[3 ]++)   ;for(C (1)=0;   (C(
        2)   =C(1       ))<C (0);)   {(*C) [2]=C   [2][
        1]  -49;        c=(* C[2]<=   63); c=(*   C)[0]
        -4  *(C[        3][0 ]=105-  C[2][ c]   -7*(*(C
        [2]+c)<         'c') -18*(  C[2][c    ]<77)+2*(
         *C)[4          ]-7* (C[2] [c]<'C'  ))-6;for(C(
        3)=0;
       C(3)<                                (*C[2]?*C[2
      ]>'r'                             ?C[    2][1]:(1
     +2*(*C             [2]>   64)    +(2-!C[2    ][3])
    *(58 ==             (*(C         +2))[0])-
    (C[2] [0            ]=='m'   )  ):C(2)?C(0     )-C(
  2):0  );C(3)++)       C(1)+=c(C  [1][4]|(*     C[2]&&
 *C[2  ]<'s'?*C[2]      ==58?C(3)  ==1?**C     >17&&**C
 <51  ?C[ 2]    [1]     ==59?39:  C[2][1     ]==58?9:1:
0:0  :63  >*     C[2    ]?(c<7&&  c>-9?C[1    ][(*C[2]<
45?  'c'  *5     +2*    '%':*C[   2]<  61?570    :571)+
3*c  ]:   0)      :*C   [2]>'o'  ?**C>26&&**C<29    &&!
(*C  )[    2]     ||(   *C)[2]  ==1&&(&*C[0])       [0]
 <34  &&   31     <**   C?C(3)  <2?15+225*C(3     ):0:(
 *C)[  2]  ==     3?C   (3)<2  &&**C>22&&**C     <45&&C
 (3)<      2?     C[    1][7*  *(*C)+151+C      (3)]:0:
  7==(     *C    )[2    ]&&*  *C>26&&**C       <42&&C(3
  )<2?C    [1   ][7     ***C  +135+C(3)]       :0:*C[2]
   <'k'?    (c >-5                      &&      c<5?C(3
    )<2?C   [1][(                       (*C)     [2]<3?
     207:205)+7*                        c+C(3     )]:C[
      2][2]==46               &&        (c==-2||   c==-
            1-                          2*(*C[3]%2  ))?
            96                          :0:0)|((*C)[2
             ]?
             C(         3      )        ?C(3)< 2
             &&                        *C[3]>  7   &&
             c<           1&&c  >-24  ?8:0:*   C
             [3         ]<8&&c  >1   &&c<24    ?   ' '
        :0   :0)        |(C(3) <2     &&(  **  C
       ==66   &&        *C[3   ]>14   ||*  C[  3
       ]>12   &&        58   ==**C||   *
       C[3    ]<        2  &&**C==10   )            ?
        5*  51:                       0)|(7==  (
         *C)[                        2]?*C[3]  <
8?c>13&& c<23&&C(3)<2?C
[1][144+ 7*c+C(3)]:0:C(
3) && c< -14&&c>- 24?C[
1] [7 *c +400+C(3 )]:0:
0) :! C  (3)?**C> 21&&C
[0 ][    0]   <32
?C     [ 1 ]   [(
*   C )    [2   ] +323
   +7     **   *C ]:36
 + 1   < **   C&& '0'>
*     *C ?  C[1][
   C[ 2]  [2]+162
 + 7* **C]:0:0:0));C[1
][ 3] ++;C[2]+=3;}c(0)
;C [3 ]-=2;}*C[3]=0;}}
